---
title: | 
  | Title (line 1)
  | Title (line 2)
short-title: "Short Title"
author: "Author Name"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
bibliography: "reference.bib"
output: 
  beamer_presentation:
    includes:
      in_header: uscstyle.tex
  fonttheme: "structurebold"
  latex_engine: xelatex
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_bw())
```

# Section 1

## Slide 1

1. **bolding**, *italicizing*

2. Putting a citation [@r2022]

3. Putting an equation $\hat\beta = .3, 95\% \text{ CI} = [.1, .5]$
    * Second level bullet item

This is the beginning of a sentence. 
How it looks without a "\\break". 
\break
How it looks after a "\\break". 
\
How it looks after a "\\". 

\break
How it looks after an extra line and a "\\break". 

\
How it looks after an extra line and a "\\". 
    
## Slide 2

```{r echo=FALSE, fig.height = 2, fig.width = 3, fig.align='center'}
x <- rnorm(1000, mean = .5, sd = 1)
ggplot(data.frame(x = x), aes(x = x)) + 
  geom_histogram(binwidth = .1)
```

Mean of the above distribution is `r mean(x)`. 

## Slide 3

:::: {.USCbox data-latex=""}
::: {.center data-latex=""}
Chunk title
:::
Chunk with emphasis
::::


## References {.allowframebreaks}






